Global study of well-being and internet adoption | Online analysis supplement

### 2021-11-22 03-model-estimate.Rmd
Estimate models 1 & 2

# MCMC settings
options(brms.backend = "cmdstanr")
hmc <- list(
  chains = 4,
  cores = 4,
  threads = 3,
  iter = 1500, 
  warmup = 750,
  refresh = 10,
  adapt_delta = .90, 
  max_treedepth = 10
)
```

@@

```{r}
# Define models of outcomes
bf_1 <- bf(
  val ~ 
    year * sex * age + 
    (year * sex * age |c| country) +
    (year * sex * age |r| region),
  family = gaussian()
)

bf_1_se <- bf(
  val | resp_se(se, sigma = TRUE) ~ 
    year * sex * age + 
    (year * sex * age |c| country) +
    (year * sex * age |r| region),
  family = gaussian()
)
```

```{r}
fits_1 <- dat %>%
  group_by(cause) %>% 
  summarise(
    fit = list(
      brm(
        formula = bf_itu + bf_1 + set_rescor(FALSE), 
        data = cur_data_all(),
        chains = hmc$chains, 
        cores = hmc$cores, 
        threads = hmc$threads,
        iter = hmc$iter, 
        warmup = hmc$warmup, 
        refresh = hmc$refresh,
        control = list(
          adapt_delta = hmc$adapt_delta, 
          max_treedepth = hmc$max_treedepth
        ),
        file = str_glue("output/brm-1-{cur_group()}")
      )
    )
  )

fits_1 <- dat %>%
  group_by(cause) %>% 
  summarise(
    fit_se = list(
      brm(
        formula = bf_itu + bf_1_se + set_rescor(FALSE), 
        data = cur_data_all(),
        chains = hmc$chains, 
        cores = hmc$cores, 
        threads = hmc$threads,
        iter = hmc$iter, 
        warmup = hmc$warmup, 
        refresh = hmc$refresh,
        control = list(
          adapt_delta = hmc$adapt_delta, 
          max_treedepth = hmc$max_treedepth
        ),
        file = str_glue("output/brm-1-se-{cur_group()}")
      )
    )
  )
```

@@

```{r}
fits_1 %>% 
  mutate(
    out = map(
      fit, 
      ~as_draws_df(.x, variable = "^b_", regex = TRUE) %>% 
        summarise_draws(
          mean, quantile, rhat, 
          .args = list(probs = c(.025, .975))
        )
    )
  ) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  mutate(across(where(is.numeric), ~round(., 2))) %>% 
  mutate(
    result = str_glue(
      "{mean} ({`2.5%`}, {`97.5%`}) [rh = {round(rhat, 1)}]"
    )
  ) %>% 
  select(-c(mean, `2.5%`, `97.5%`, rhat)) %>% 
  pivot_wider(names_from = model, values_from = result) %>% 
  kbl() %>% 
  kable_paper(html_font = Font)
```

@@

```{r}
bf_2 <- bf(
  val ~ 
    year * sex + year * age + i1_cw * sex + i1_cw * age + i1_cb + 
    (year * sex + year * age + i1_cw * sex + i1_cw * age | country) +
    (year * sex + year * age + i1_cw * sex + i1_cw * age | region),
  family = gaussian()
)

bf_2_se <- bf(
  val | se(se, sigma = TRUE) ~ 
    year * sex * age + i1_cw * sex * age + i1_cb + 
    (year * sex * age + i1_cw * sex * age | country) +
    (year * sex * age + i1_cw * sex * age | region),
  family = gaussian()
)

@@

fits_2 <- dat %>%
  group_by(cause) %>% 
  summarise(
    fit_se = list(
      brm(
        formula = bf_2_se, 
        data = cur_data_all(),
        chains = hmc$chains, 
        cores = hmc$cores, 
        threads = hmc$threads,
        iter = hmc$iter, 
        warmup = hmc$warmup, 
        refresh = hmc$refresh,
        control = list(
          adapt_delta = hmc$adapt_delta, 
          max_treedepth = hmc$max_treedepth
        ),
        file = str_glue("output/brm-2-se-{cur_group()}")
      )
    )
  )
```

>>>>

# MCMC settings
options(brms.backend = "cmdstanr")
hmc <- list(
  chains = 4,
  cores = 4,
  threads = 3,
  iter = 2000, 
  warmup = 1000,
  refresh = 50,
  adapt_delta = .90, 
  max_treedepth = 10
)
```

@@

```{r}
# Define models of outcomes
bf_1 <- bf(
  val ~ 
    year * sex + year * age + 
    (year * sex + year * age |c| country) +
    (year * sex + year * age |r| region),
  family = gaussian()
)

bf_1_se <- bf(
  bf(val | resp_se(se, sigma = TRUE) ~ 
       year * sex + year * age +
       (year * sex + year * age |c| country) +
       (year * sex + year * age |r| region),
     sigma ~ 1
  ),
  family = brmsfamily("gaussian", link = "log", link_sigma = "log")
)
```

```{r}
fits_1 <- dat_model1 %>%
  group_by(cause) %>% 
  summarise(
    fit = list(
      brm(
        formula = bf_itu + bf_1 + set_rescor(FALSE), 
        data = cur_data_all(),
        chains = hmc$chains, 
        cores = hmc$cores, 
        threads = hmc$threads,
        iter = hmc$iter, 
        warmup = hmc$warmup, 
        refresh = hmc$refresh,
        control = list(
          adapt_delta = hmc$adapt_delta, 
          max_treedepth = hmc$max_treedepth
        ),
        file = str_glue("output/brm-1-{cur_group()}")
      )
    )
  )

# fits_1 <- dat_model1 %>%
#   group_by(cause) %>% 
#   summarise(
#     fit_se = list(
#       brm(
#         formula = bf_itu + bf_1_se + set_rescor(FALSE), 
#         data = cur_data_all(),
#         chains = hmc$chains, 
#         cores = hmc$cores, 
#         threads = hmc$threads,
#         iter = hmc$iter, 
#         warmup = hmc$warmup, 
#         refresh = hmc$refresh,
#         control = list(
#           adapt_delta = hmc$adapt_delta, 
#           max_treedepth = hmc$max_treedepth
#         ),
#         file = str_glue("output/brm-1-se-{cur_group()}")
#       )
#     )
#   )
```

@@

```{r}
fits_1 %>% 
  mutate(
    out = map(
      fit, 
      ~as_draws_df(.x, variable = "^b_", regex = TRUE) %>% 
        summarise_draws(
          mean, quantile, rhat, 
          .args = list(probs = c(.025, .975))
        )
    )
  ) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  mutate(across(where(is.numeric), ~round(., 2))) %>% 
  mutate(
    result = str_glue(
      "{mean} ({`2.5%`}, {`97.5%`}) [rh = {round(rhat, 1)}]"
    )
  ) %>% 
  select(-c(mean, `2.5%`, `97.5%`, rhat)) %>% 
  pivot_wider(names_from = cause, values_from = result) %>% 
  kbl() %>% 
  kable_paper(html_font = Font)
```

@@

```{r}
bf_2 <- bf(
  val ~ 
    year * sex + year * age + i1_cw * sex + i1_cw * age + i1_cb + 
    (year * sex + year * age + i1_cw * sex + i1_cw * age + i1_cb | country) +
    (year * sex + year * age + i1_cw * sex + i1_cw * age + i1_cb | region),
  family = gaussian()
)

bf_2_se <- bf(
  bf(val | resp_se(se, sigma = TRUE) ~ 
       year * sex + year * age + i1_cw * sex + i1_cw * age + i1_cb + 
       (year * sex + year * age + i1_cw * sex + i1_cw * age + i1_cb | country) +
       (year * sex + year * age + i1_cw * sex + i1_cw * age + i1_cb | region),
     sigma ~ 1
  ),
  family = brmsfamily("gaussian", link = "log", link_sigma = "log")
)

@@

# fits_2 <- dat %>%
#   group_by(cause) %>% 
#   summarise(
#     fit_se = list(
#       brm(
#         formula = bf_2_se, 
#         data = cur_data_all(),
#         chains = hmc$chains, 
#         cores = hmc$cores, 
#         threads = hmc$threads,
#         iter = hmc$iter, 
#         warmup = hmc$warmup, 
#         refresh = hmc$refresh,
#         control = list(
#           adapt_delta = hmc$adapt_delta, 
#           max_treedepth = hmc$max_treedepth
#         ),
#         file = str_glue("output/brm-2-se-{cur_group()}")
#       )
#     )
#   )
```
